---
title: "R markdown example"
author: "William Robson"
date: "26/04/2021"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Viewing and summarising the data

Below is the data summary for the 1st question of the meta-analysis assignment for BIO8075. We first need to activate the r packages, which are displayed below:

```{r message=FALSE}
library(metafor)
library(mosaic)
```

Loading in the data and viewing it

```{r } 
Q1.dat <- read.csv("Q1.csv")

summary(Q1.dat)
```
As can be seen the data is in a continious format. We still need the vi and yi variables (Hedge's g and within variance) to carry out further analysis. We use the escalc function of the metafor package and then assign the correct measures to the function (as seen below).
``` {R}
continuous <- escalc(measure="SMD", m1i=mean_control, sd1i=SD_control, n1i=sample_size_control,
                         m2i=mean_invaded, sd2i=SD_invaded, n2i=sample_size_invaded, data=Q1.dat)

summary(continuous)
```
Now we can finally do random meta-analysis with this data 

``` {R}
continuous_random_rma <- rma(yi, vi, data=continuous)

summary(continuous_random_rma)
```
We get an overall effect size of 0.53 and confidence intervals ranging from 0.12 - 0.9. We also generate a p-value of 0.0106, indicating signifcant differences.

## Plotting the data

Now we have carried out the meta-analysis, we want to view it on a forest plot, a Q-Q plot and a funnel plot to look for publication bias

## Forest plot

```{r }
forest(continuous_random_rma, showweights = TRUE, slab=continuous$lastname)
```

## Quantile to Quantile plot

``` {r}
qqnorm(continuous_random_rma, main="Random normal QQ plot")
```

## Bias prediction

```{r continuous, echo=TRUE}
continuous_funnel <- rma(yi, vi, data=continuous)

continuous_trimfill <- trimfill(continuous_funnel)

funnel(continuous_trimfill, level=c(90, 95, 99),
       shade=c("white", "gray", "darkgray"),
       refline=0)
```
